%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Thanks : Rishi Shah 's Contribution
% inspired by his awesome contribution:
% https://www.overleaf.com/articles/rishi-shahs-resume/vgxvkmxktyxn
% Author : Allianzcortex
% contact me : github.com/Allianzcortex
% email : iamwanghz#gmail.com
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{blindtext}

\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }
    
\urlstyle{same}


\usepackage[left=0.40in,top=0.4in,right=0.40in,bottom=0.4in]{geometry} % Document margins
\usepackage{fontawesome}
\usepackage{times}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
% \begin{center}
% {\centerline {\em \textbf {Seeking for a fulltime internship from Sep 2019 - Apr 2010(8 months) } } }
% \end{center}
\name{Zeyong Jin} % Your name 



\address{\faPhone \, (778) 316-8193 \: \: \faEnvelope{ zeyongj@gmail.com} \: \: \faGithub{ \url{https://github.com/zeyongj}} \: \: \faLink{ \url{https://www.zeyongjin.net/}}}
\address{\faMapMarker{ 2309 - 2108 Gilmore Avenue, Burnaby, V5C 0N8, Canada}} 

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Simon Fraser University} \hfill {\em Sep 2018 - Apr 2022} 
\\{ \textit {Bachelor of Science (with Distinction)}} \hfill {Burnaby, BC} 
\begin{itemize}
  \vspace{-0.2cm}\item \textbf{Program}: Major in Computing Science, Concentration in Information Systems, Minor in Mathematics.
  \vspace{-0.2cm}\item \textbf{Grade}: Cumulative GPA of 3.62.
  \vspace{-0.2cm}\item \textbf{Related Courses}: Data Structures, Algorithms, Computer Systems, Operating Systems, Software Engineering, Requirements Engineering, Database Systems, Natural Language Processing, Computational Data Science, Data Mining.
\end{itemize}

{\bf Fraser International College} \hfill {\em May 2017 - Apr 2018} 
\\{ \textit {UTP Stage II:  Science}} \hfill {Burnaby, BC} 
\begin{itemize}
  \vspace{-0.2cm}\item \textbf{Program}: Major in Computing Science.
  \vspace{-0.2cm}\item \textbf{Grade}: Cumulative GPA of 3.92.
  \vspace{-0.2cm}\item \textbf{Award}: Dean’s Honour Roll \textit{(2017 Summer)}.
  % \vspace{-0.2cm}\item \textbf{Related Courses}: C++ Programming, Calculus, Discrete Mathematics, Linear Algebra.
\end{itemize}


\end{rSection}

\begin{rSection}{Technical Skills}
\begin{itemize}
    \item \textbf{Programming Languages}:  C, C++, Java, Python, R, Assembly, JavaScript.
    \vspace{-0.2cm}\item \textbf{IDEs \& Development Tools}: Microsoft Visual Studio, IntelliJ IDEA, Android Studio, PyCharm, R Studio, Google Colab, Jupyter Notebook.
    \vspace{-0.2cm}\item \textbf{Database Systems}: Microsoft SQL Server 2018, MySQL.
    \vspace{-0.2cm}\item \textbf{Operating Systems}: Linux \textit{(Ubuntu)}, Windows.
    \vspace{-0.2cm}\item \textbf{Version Control Tools}: Git \textit{(GitLab, GitHub)}.
    \vspace{-0.2cm}\item \textbf{UI/UX Design Tools}: Balsamiq, Figma.
    \vspace{-0.2cm}\item \textbf{Documentation \& Office Tools}: \LaTeX, R Markdown, Microsoft Office Suite \textit{(Word, Excel, PowerPoint)}.
    \vspace{-0.2cm}\item \textbf{Certificates}: Machine Learning Specification \textit{(Provided by Stanford University on Coursera)}; Data Science in Python, Applied Machine Learning in Python \textit{(Provided by the University of Michigan on Coursera)}.
\end{itemize}

\end{rSection}

\begin{rSection}{Transferable Skills}
\begin{itemize}
    % \item \textbf{Execution Ability}: Proficient in translating strategies and ideas into actionable plans and executing them.
    \item \textbf{Communication \& Teamwork}: Excelled in leading diverse teams, fostering collaboration and persuading peers.
    \vspace{-0.2cm} \item \textbf{Time Management}: Consistently meets deadlines through effective prioritization and planning.
    \vspace{-0.2cm} \item \textbf{Continuous Learning}: Possesses a strong curiosity and openness to acquiring new knowledge and skills.
    \vspace{-0.2cm} \item \textbf{Languages}: Bilingual in Mandarin \textit{(Native)} and English \textit{(Proficient)}.
    % \vspace{-0.2cm} \item \textbf{Interests}: Enjoys reading, writing, cultural immersion and historical site exploration in leisure time.
\end{itemize}
\end{rSection}


\begin{rSection}{Publication}

\begin{itemize}
    \item \textbf{Z. Jin}, J. Zhao, Z. Qian, L. Cao, Y. Wang, Y. Ding, Y. Hu, Z. Zhang.
    \textit{Role-Play Paradox in Large Language Models: Reasoning Performance Gains and Ethical Dilemmas.}  
    Submitted to \textit{The 47th Annual Meeting of the Cognitive Science Society (CogSci 2025)}, 2025.  
    Available at: \href{https://doi.org/10.48550/arXiv.2409.13979}{arXiv:2409.13979 [cs.CL]}.
\end{itemize}

\end{rSection}

\begin{rSection}{Academic Research}

{\bf Role-Play Paradox in Large Language Models: Reasoning Performance Gains and Ethical Dilemmas} \hfill {\em Oct 2024 - Jan 2025}  
\begin{itemize}
    \vspace{-0.2cm} \item Investigated the effects of role-playing in large language models \textit{(LLMs)} on reasoning performance and ethical risks, revealing that role simulation enhances problem-solving but also amplifies biases and toxicity.  
    \vspace{-0.2cm}\item Designed and conducted empirical evaluations on GPT-4, GPT-3.5, and Mixtral-8x7B using stereotype and toxicity benchmarks \textit{(CrowS-Pairs, StereoSet, HarmfulQ)}, demonstrating how automated role assignment exacerbates biases.  
    \vspace{-0.2cm}\item Co-authored a research paper submitted to \textit{CogSci 2025}, contributing to AI ethics literature on bias mitigation and safe deployment of LLMs in high-stakes applications.  
\end{itemize}

\end{rSection}


\begin{rSection}{Professional EXPERIENCES}

{\bf Rancho Management Services (B.C.) Ltd.} \hfill {\em Dec 2024 - Present}  
\\{\textit{Accounts Payable Supervisor} \hfill {Vancouver, BC}}  
\begin{itemize}
    \vspace{-0.2cm}
    \item Developed a cheque tracking platform to streamline accounts payable operations by automating cheque status updates, reconciliation, and reporting processes. Developed using JavaScript, and integrated into the department's workflow, with source code available on GitHub \url{https://github.com/zeyongj/Cheque-Tracking}.  
    \vspace{-0.2cm}
    \item Enhanced the department’s payment processing system by creating automated tools in Python to generate detailed payment reports, improving data accuracy and processing speed by 20\%.  
    \vspace{-0.2cm}
    \item Oversaw invoice processing, vendor payments, and reconciliation of accounts to ensure timely and accurate financial transactions while maintaining compliance with company policies and accounting standards.  
\end{itemize}



{\bf Rancho Management Services (B.C.) Ltd.} \hfill {\em Apr 2024 - Dec 2024} 
\\{\textit{Accounts Payable Clerk} \hfill {Vancouver, BC}}
\begin{itemize}
    \vspace{-0.2cm}\item Engineered Python-based automation to monitor over 10,000 invoices from over 2,000 vendors, achieving a 40\% reduction in manual file handling and improving data aggregation efficiency by 60\%.
    \vspace{-0.2cm}\item Built a dynamic programming solution to optimize invoice payment processing, ensuring fund allocation while maintaining reserve requirements. Implemented logic to prioritize payments based on invoice classifications and available cash flow.
    \vspace{-0.2cm}\item Streamlined financial operations by integrating automated data entry and validation tools, reducing manual errors and enhancing the accuracy of payment records through robust data analysis and reporting.
\end{itemize}

{\bf Simon Fraser University} \hfill {\em Jan 2021 - Dec 2021} \\
{\textit{Teaching Assistant} \hfill {Burnaby, BC}}
\begin{itemize}
    \vspace{-0.2cm}\item Facilitated grading processes using Crowdmark for the course STAT 203 \textit{(Introduction to Statistics for the Social Sciences)}, providing prompt and constructive feedback to students and instructors \textit{(Spring Term)}.
    \vspace{-0.2cm}\item Assisted in grading assignments and exams via Canvas for the course CMPT 115 \textit{(Exploring Computer Science)}, ensuring timely feedback to both students and faculty \textit{(Fall Term)}.
    \vspace{-0.2cm}\item Hosted weekly online office hours, addressing undergraduate queries related to computing science. Addressed student inquiries regarding grading, ensuring all responsibilities were completed punctually.
    \vspace{-0.2cm}\item Contributed to the Department of Statistics and Actuarial Science, working alongside Dr. Harsha Perera and Mr. Scott Pai. Supported the School of Computing Science under the supervision of Dr. Diana Cukierman.
\end{itemize}

\end{rSection}



\begin{rSection}{Academic Projects}


{\bf Prompt-based Text Matching Methods for Fake News Stance Detection} \hfill {\em Sep 2021 - Dec 2021} 
\\{\textit{CMPT 413: Computational Linguistics; Supervised by Prof. Angel Chang} \hfill {Burnaby, BC}}
\begin{itemize}
    \vspace{-0.2cm} \item Leveraged the Bidirectional Encoder Representations from Transformers \textit{(BERT)} model to analyze the stance relationship between news headlines and their corresponding articles.
    \vspace{-0.2cm} \item Fine-tuned the BERT model for enhanced accuracy in detecting stance relationships, achieving a notable accuracy of 90.37\% on the Fake News Competition \textit{(FNC)} dataset.
    \vspace{-0.2cm} \item Benchmarked the BERT-based model against four baseline algorithms, highlighting its superior performance in fake news classification.
    \vspace{-0.2cm} \item Project repository and detailed documentation available at \url{https://github.com/zeyongj/Fake-News-Stance-Detection}. A comprehensive presentation can be viewed at \url{https://www.youtube.com/watch?v=DtKjSMv31RQ&ab_channel=ZeyongJin}.
\end{itemize}

{\bf COVID-19 Patient Outcome Prediction} \hfill {\em Jan 2021 - Apr 2021}  
\\{\textit{CMPT 459: Data Mining; Supervised by Prof. Martin Ester} \hfill {Burnaby, BC}}  
\begin{itemize}
    \vspace{-0.2cm} \item Built and optimized predictive models for COVID-19 patient outcomes using LightGBM, Support Vector Machine \textit{(SVM)}, and Multilayer Perceptron \textit{(MLP)}, achieving 0.8840 accuracy and 0.8391 F1-score with LightGBM.  
    \vspace{-0.2cm} \item Engineered new features and applied hyperparameter tuning to improve model performance, handling imbalanced data effectively.  
    \vspace{-0.2cm} \item Project repository available at \url{https://github.com/zeyongj/Prediction-of-The-Outcome-of-A-COVID-19-Patient}.  
\end{itemize}

{\bf Practical Parent Application} \hfill {\em Sep 2020 - Dec 2020}  
\\{\textit{CMPT 276: Introduction to Software Engineering; Supervised by Dr. Brian Fraser} \hfill {Burnaby, BC}}  
\begin{itemize}
    \vspace{-0.2cm} \item Developed an Android application in Android Studio for task delegation among children, including a coin-flip feature for fair task assignment.  
    \vspace{-0.2cm} \item Integrated a real-time task tracking system and a breathing rhythm regulator to enhance user engagement.  
    \vspace{-0.2cm} \item Project repository available at \url{https://github.com/zeyongj/Pratical-Parent-Application}.  
\end{itemize}

% {\bf COVID-19 Patient Outcome Prediction} \hfill {\em Jan 2021 - Apr 2021} 
% \\{\textit{CMPT 459: Data Mining; Supervised by Prof. Martin Ester} \hfill {Burnaby, BC}}
% \begin{itemize}
%     \vspace{-0.2cm}\item Engineered a predictive model to determine potential outcomes, namely recovered, hospitalized and non-hospitalized for COVID-19 patients.
%     \vspace{-0.2cm}\item Presented data visualizations, including a global heatmap of confirmed cases and comprehensive attribute statistics from datasets.
%     \vspace{-0.2cm}\item Built, evaluated, and proceeded parameter tunning on classifiers of Light Gradient Boosting Machine \textit{LightGBM}, Support Vector Machine \textit{(SVM)} and Multilayer Perceptron \textit{(MLP)}. Achieved highest accuracy of 0.8840 and F1 score of 0.8391 with LightGBM.
%     \vspace{-0.2cm}\item Project available at \url{https://github.com/zeyongj/Prediction-of-The-Outcome-of-A-COVID-19-Patient}.
% \end{itemize}

% {\bf Practical Parent Application} \hfill {\em Sep 2020 - Dec 2020} 
% \\{\textit{CMPT 276: Introduction to Software Engineering; Supervised by Dr. Brian Fraser} \hfill {Burnaby, BC}}
% \begin{itemize}
%     \vspace{-0.2cm}\item Developed an Android application in Android Studio to assist parents in task delegation among children, incorporating features like a coin-flip game for fair task assignment.
%     \vspace{-0.2cm}\item Integrated real-time task status tracking and a unique breathing rhythm regulator to guide parents in structured breathing exercises, enhancing user experience and utility.
%     \vspace{-0.2cm}\item Collaborated in a team of four, leveraging agile methodologies for iterative development, and produced comprehensive user stories and development documentation.
%     \vspace{-0.2cm}\item Project with detailed documentation and code available at \url{https://github.com/zeyongj/Pratical-Parent-Application}.
% \end{itemize}


% {\bf Improving Dijkstra's Algorithm} \hfill {\em Sep 2019 - Dec 2019}
% \\{\textit{CMPT 307: Data Structures and Algorithms} \hfill {Burnaby, BC}}
% \begin{itemize}
%     \vspace{-0.2cm}\item Found the shortest distance and path of any two places in a city using Dijkstra’s, A* and Landmark Algorithms and showed the savings if A* and Landmark Algorithms are used.
%     \vspace{-0.2cm}\item Exported all the results as a text file.
%     \vspace{-0.2cm}\item Coded in C++ via the integrated development environment of Microsoft Visual Studio 2017, and instructed by Prof. Binay Bhattacharya. Project available at \url{https://github.com/zeyongj/Improving-Dijkstra-Algorithm}.
% \end{itemize}

\end{rSection}



\begin{rSection}{Personal Projects}

{\bf ConnectX Agent} \hfill {\em Sep 2024 - Oct 2024}
\\{\textit{Kaggle Competition} \hfill {Vancouver, BC}}
\begin{itemize}
    \vspace{-0.2cm}\item Developed a custom agent utilizing the Minimax algorithm with Alpha-Beta Pruning to compete in the ConnectX Kaggle competition, focusing on strategic decision-making and efficient exploration of the game tree.
    \vspace{-0.2cm}\item Designed and implemented a heuristic evaluation function to assess board states, considering factors such as control of the center column, potential winning sequences, and threats posed by the opponent.
    \vspace{-0.2cm}\item Achieved a highest score of over 920, ranking 7th among over 100 participants, demonstrating strong algorithmic performance and effective decision-making in real-time gameplay scenarios. Project repository available at \url{https://github.com/zeyongj/ConnectX-Agent}.
\end{itemize}

{\bf Loan Approval Prediction} \hfill {\em Sep 2024 - Oct 2024}
\\{\textit{Kaggle Competition} \hfill {Vancouver, BC}}
\begin{itemize}
    \vspace{-0.2cm}\item Achieved a top 30\% ranking in the Kaggle Playground Series competition focused on loan approval prediction, demonstrating strong model performance.
    \vspace{-0.2cm}\item Applied LightGBM with extensive hyperparameter tuning using Optuna, resulting in a final ROC-AUC score of 0.96025, significantly improving over initial benchmarks.
    \vspace{-0.2cm}\item Created new features to enhance model predictive power and addressed class imbalance using SMOTE, ensuring robust classification results. Project repository available at \url{https://github.com/zeyongj/Loan-Approval-Prediction}.
\end{itemize}



% {\bf Advanced House Price Prediction} \hfill {\em Jan 2023 - Apr 2023}
% \\{\textit{Kaggle Project} \hfill {New Westminster, BC}}
% \begin{itemize}
%     \vspace{-0.2cm}\item Developed an ensemble machine learning model to predict house prices using the Ames Housing dataset. The model employed a stacking technique with RandomForestRegressor, XGBRegressor, and Lasso as base models and a final estimator Lasso model. Project available at \url{https://github.com/zeyongj/House-Prices-Advanced-Regression-Techniques}.
%     \vspace{-0.2cm}\item Implemented an effective preprocessing pipeline to handle both numerical and categorical data. Conducted comprehensive exploratory data analysis to discover underlying trends and patterns, informing feature engineering and selection strategies.
%     % \vspace{-0.2cm}\item Leveraged GridSearchCV for hyperparameter tuning and KFold cross-validation for model evaluation. Achieved a competitive mean RMSE score, identifying opportunities for further model enhancement, such as extensive feature selection and advanced ensemble methods.
%     % \vspace{-0.2cm}\item Coded in Python. Project available at \url{https://github.com/zeyongj/House-Prices-Advanced-Regression-Techniques}.
% \end{itemize}

% {\bf Countdown Timer Application} \hfill {\em Sep 2020 - Oct 2020} 
% \\{\textit{Android Development Project} \hfill {New Westminster, BC}}
% \begin{itemize}
%     \vspace{-0.2cm}\item Crafted an intuitive Android application enabling users to set customizable countdown timers, with real-time display of remaining time.
%     \vspace{-0.2cm}\item Implemented an alert system to notify users with an alarm upon timer completion, enhancing user experience.
%     \vspace{-0.2cm}\item Developed in Java using Android Studio. Code at \url{https://github.com/zeyongj/Count-Down-Timer-Android-App}.
% \end{itemize}


\end{rSection}

\end{document}
